Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-23 paper.tex
Addresses point 3 in review #25B

In the context of both deadlines and dependencies coupled with packet loss, partial reliability
requires application-level framing \cite{clark:1990:architecture} to
make the best use of payload data. At the transport
layer, this implies a \emph{message oriented} service, that
maintains application data unit (ADU) boundaries.

@@

At the receiver, segments are passed to the kernel, where they are
initially processed as under standard TCP: duplicate acknowledgements are
generated for out-of-order segments, for example. After this, a metadata
entry is created, and placed in FIFO queue. When the intermediary layer
reads from the socket, it receives the segment associated with the
metadata entry at the head of the queue, with its TCP sequence number
attached.

At the intermediary layer on the receiver, incoming segments are scanned
for complete messages (i.e., data between two zero bytes), which are
decoded and passed to the application. Any message fragments are buffered,
alongside their TCP sequence number, awaiting the arrival of the remainder
of the message. Once the message has been reassembled, it is decoded, and
delivered to the application.
\todo{Review B: Head-of-line blocking problem not introduced, so not clear
why this mechanism is needed.}
% TCP Hollywood inherits standard TCP's congestion control mechanism.
% Clearly, being a loss-based algorithm, this is not appropriate for
% real-time applications.
% \todo{discuss how we need to change TCP congestion control}

>>>>

In the context of both deadlines and dependencies coupled with packet loss, partial reliability
requires application-level framing \cite{clark:1990:architecture} to
make the best use of payload data. At the transport
layer, this implies a \emph{message oriented} service, that
maintains application data unit (ADU) boundaries. Messages are delivered to
the application in the order they arrive. For example, the combination of
reliability and in-order delivery in TCP can introduce significant latency:
incoming segments may be head-of-line blocked waiting for the delivery of
an earlier segment.

@@

At the receiver, segments are passed to the kernel, where they are
initially processed as under standard TCP: duplicate acknowledgements are
generated for out-of-order segments, for example. After this, a metadata
entry is created, and placed in FIFO queue. When the intermediary layer
reads from the socket, it receives the segment associated with the
metadata entry at the head of the queue, with its TCP sequence number
attached. This means that segments are delivered in the order that they
arrive, removing the latency associated with head-of-line blocking in TCP
\cite{mcquistin2016tcp}.

At the intermediary layer on the receiver, incoming segments are scanned
for complete messages (i.e., data between two zero bytes), which are
decoded and passed to the application. While the segments are sent
containing only one message, these may be resegmented or coalesced in the
network. A segment may arrive containing \emph{fragments} of message
data. These fragments are buffered, alongside their TCP sequence number, 
awaiting the arrival of the remainder of the message. Once the message has
been reassembled, it is decoded, and delivered to the application.
% TCP Hollywood inherits standard TCP's congestion control mechanism.
% Clearly, being a loss-based algorithm, this is not appropriate for
% real-time applications.
% \todo{discuss how we need to change TCP congestion control}
